Equalizer\\Programming and User Guide

### 2010-12-22 Developer/ProgrammingGuide/paper.tex
Fix link in presentation
[ ] May break build
[ ] Breaks existing applications
[x] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

{\footnotesize\lstinputlisting[firstline=154, lastline=169]
  {../../../src/examples/eqPly/eqPly.cpp}}

@@

{\footnotesize\lstinputlisting[firstline=171, lastline=179]
  {../../../src/examples/eqPly/eqPly.cpp}}

>>>>

{\footnotesize\lstinputlisting[firstline=154, lastline=165]
  {../../../src/examples/eqPly/eqPly.cpp}}

@@

{\footnotesize\lstinputlisting[firstline=167, lastline=175]
  {../../../src/examples/eqPly/eqPly.cpp}}
